method

### 2022-01-27 06_Paper/ER-ED/method.Rmd
fixed anova issue

aov_arousalView = afex::aov_ez(id = "ID",
                           dv = "arousal",
                           data = arousal_view,
                           within = "block",
                           fun_aggregate = mean) 
afex::nice(aov_arousalView, es = "pes")

@@

aov_arousalReg = afex::aov_ez(id = "ID",
                              dv = "arousal",
                              data = arousal_reg,
                              within = "block",
                              fun_aggregate = mean)
afex::nice(aov_arousalReg, es = "pes")

@@

aov.effort = afex::aov_ez(id = "ID",
                          dv = "effort",
                          data = effort_reg,
                          within = "block",
                          fun_aggregate = mean)
afex::nice(aov.effort, es = "pes")

>>>>

aov_arousalView = afex::aov_ez(data = arousal_view,
                               id = "ID",
                               dv = "arousal",
                               within = "block",
                               fun_aggregate = mean,
                               include_aov = TRUE)

@@

aov_arousalReg = afex::aov_ez(data = arousal_reg,
                              id = "ID",
                              dv = "arousal",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)
afex::nice(aov_arousalReg, es = "pes")

@@

aov.effort = afex::aov_ez(data = effort_reg,
                          id = "ID",
                          dv = "effort",
                          within = "block",
                          fun_aggregate = mean,
                          include_aov = TRUE)
afex::nice(aov.effort, es = "pes")
